Arrangement for DroneGo

### 2020-03-09 PAPER.tex
Updates from Overleaf

@@

%要改
    \item Variance contribution rate (${k_i}$) of public factor &{F_i}&

    \item Factor load matrix

    \ttem Factor variable score

@@

@@

\begin{equation}\label{ct}
    insert equation
\end{equation}

@@

%公式2
\begin{equation}
    insert
\end{equation}

@@

\begin{equation}\label{ft}
    insert
\end{equation}

$a_0$ and $b$ in the function can be adjusted appropriately according to the measured carbon dioxide emission concentration and the radiation intensity of the greenhouse effect.

@@

\begin{equation}
    insert
\end{equation}

According to scientists' estimates, the pre-industrial carbon dioxide emission concentration was $270\times10^{-6}$, and the temperature was about 0.68 degrees Celsius lower than that of 2000, which was considered zero in order to calculate sea-level changes.

@@

\begin{equation}
    insert
\end{equation}

>>>>

%行内公式加$符号

@@

    \item Standardize the data obtained
    \begin{equation}
    X_i=\frac{X_i-E\left( X_i \right)}{\sqrt{Var\left( X_i \right)}}
\end{equation}

    \item Factor model
\begin{equation}
    \begin{cases}
	X_1=a_{11}F_1+a_{12}F_2+\cdots +a_{1m}F_m+\varepsilon _1\\
	X_2=a_{21}F_1+a_{22}F_2+\cdots +a_{2m}F_m+\varepsilon _2\\
	\,\,\vdots\\
	\,\,\vdots\\
	X_n=a_{n1}F_1+a_{n2}F_2+\cdots +a_{nm}F_m+\varepsilon _n\\
    \end{cases}
\end{equation}

It can also be expressed as:

\begin{equation}
    X=AF+\varepsilon 
\end{equation}

Where F is the factor variable, A is the factor load matrix, $a_{ij}$ is the factor load; $\epsilon$ is the special factor

    \item Variance contribution rate (${k_i}$) of public factor $F_i$

    \begin{equation}
        k_i=\frac{\lambda _i}{\sum_{\gamma =1}^n{\lambda _{\gamma}}}\left( i=1,2...,n \right) 
    \end{equation}

$\lambda _i\left( \lambda _1,\lambda _2\cdots \cdots ,\lambda _n>0 \right) $
is the eigenvalue of the correlation coefficient matrix R of X.

    \item Factor load matrix
    \begin{equation}
            a_{ij}=\sqrt{\lambda _i}l_{ij}\left( i,j=1,2,...,n \right) 
    \end{equation}

\begin{equation}
    A=\left[ \begin{matrix}
	a_{11}&		\cdots&		a_{1m}\\
	\vdots&		\vdots&		\vdots\\
	a_{n1}&		\cdots&		a_{nm}\\
\end{matrix} \right] =\left[ \begin{matrix}
	\sqrt{\lambda _1}l_{11}&		\cdots&		\sqrt{\lambda _n}l_{n1}\\
	\vdots&		\vdots&		\vdots\\
	\sqrt{\lambda _1}l_{1n}&		\cdots&		\sqrt{\lambda _n}l_{nn}\\
\end{matrix} \right] 
\end{equation}

$I_{ij}$ is the correlation coefficient matrix R eigenvector.

    \item Factor variable score

    \begin{equation}
        F=AX
    \end{equation}

@@

\begin{equation}
    Y_i=F_i\times k_i
\end{equation}

@@

\begin{equation}\label{ct}
    C\left( t \right) =c_0e^{Be^{at}}
\end{equation}

@@

%公式2
\begin{equation}
    \ln C\left( t \right) =\ln c_0+B_te^{at}
\end{equation}

@@

\begin{equation}\label{ft}
    F\left( t \right) =a_0+b\ln \left[ c\left( t \right) /270 \right] 
\end{equation}

Where $a_0=1.81w/m^2$ and $b=2.95w/m^2$. $a_0$ and $b$ in the function can be adjusted appropriately according to the measured carbon dioxide emission concentration and the radiation intensity of the greenhouse effect.

@@

\begin{equation}
    T\left( t \right) =\beta t\ln \left[ \gamma tC\left( t \right)\right]
\end{equation}

In equation, $\beta=0.00593$; $\gamma =0.0114$. According to scientists' estimates, the pre-industrial carbon dioxide emission concentration was $270\times10^{-6}$, and the temperature was about 0.68 degrees Celsius lower than that of 2000, which was considered zero in order to calculate sea-level changes.

@@

\begin{equation}
    Z\left( t \right) =\left[ 4.13+2.65F\left( t \right) \right] T\left( t \right) \kappa ^{0.221}
\end{equation}
